Verifying Demonstrations

### 2019-02-28 paper/privacy-properties.tex
removes redundancies, corrects language, adds clarifications

For privacy, any temporary identifiers, such as pseudonyms, should only be 
reused when strictly necessary (by the principle of data minimization) for the 
fulfillment of verifiability properties (in \cref{verifiability-properties}) to 
prevent inference on long-term identities by repeated samples and side 
information.
We can thus summarize the desired privacy properties as follows:
\begin{requirements}[P]
\item\label{PseudonymUnlink} \emph{Pseudonym unlinkability}: given a protest 
  (identifier \cid), protesters Alice and Bob, and a pseudonym \(\pid_b\), the 
  adversary cannot tell if \(\pid_b = \pid_{\text{Alice}}\) or \(\pid_b = 
    \pid_{\text{Bob}}\), except with negligible probability.
\item\label{ProtestUnlink} \emph{Protest unlinkability}: protesters' pseudonyms 
  (\(\pid_\cid, \pid_{\cid'}\)) must be unlinkable between protests (\(\cid, 
    \cid'\)) from the adversary's perspective.
\item\label{WitnessUnlink}\emph{Witness unlinkability}:  witnesses' pseudonyms 
  (\(\wid_\pid, \wid_{\pid'}\)) must be unlinkable between protesters (\(\pid, 
    \pid'\)) from the adversary's perspective.
\end{requirements}

What these properties say is that pseudonyms must look random 
(\cref{PseudonymUnlink}) and that each pseudonym must be used at most once 
(\cref{ProtestUnlink,WitnessUnlink}).

>>>>

\begin{requirements}[P]
\item\label{PseudonymUnlink} \emph{Pseudonym unlinkability}: given a protest 
  (identifier \cid), protesters Alice and Bob, and a pseudonym \(\pid_b\), the 
  adversary cannot tell if \(\pid_b = \pid_{\text{Alice}}\) or \(\pid_b = 
    \pid_{\text{Bob}}\), except with negligible probability. And similarly with $wid$ if Alice and Bob act as witnesses.
\item\label{ProtestUnlink} \emph{Protest unlinkability}: protesters' pseudonyms 
  (\(\pid_\cid, \pid_{\cid'}\)) must be unlinkable between protests (\(\cid, 
    \cid'\)) from the adversary's perspective.
\item\label{WitnessUnlink}\emph{Witness unlinkability}:  witnesses' pseudonyms 
  (\(\wid_\pid, \wid_{\pid'}\)) must be unlinkable between protesters (\(\pid, 
    \pid'\)) from the adversary's perspective.
\end{requirements}

What these properties say is that pseudonyms must look random 
(\cref{PseudonymUnlink}) and that each psdeudonym must not be reused
more than strictly necessary for the verifiability properties 
(\cref{ProtestUnlink,WitnessUnlink}).
